Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-17 paper/arxiv/main_3_introduction.tex
use sentence-style capitalization

% Figure 1: Catalyst Performance Analysis Pipeline
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig1_pipeline.png}
    \caption{\textbf{Catalyst Performance Analysis Pipeline Integrating Volcano Plots and CNN.}
    The figure demonstrates the integrated usage of volcano plots for
    predictive assessment of existing catalysts, and the utility of CNNs
    to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
    eDOS occlusion and shifting experiments are conducted to extract chemical information from CNN model.}
    \label{main_fig1:pipeline}
\end{figure}

>>>>

% Figure 1: Catalyst Performance Analysis Pipeline
\begin{figure}[htbp]
    \centering
    \includegraphics[width=\textwidth]{main_fig1_pipeline.png}
    \caption{\textbf{Catalyst performance analysis pipeline integrating volcano plots and CNN.}
    The figure demonstrates the integrated usage of volcano plots for
    predictive assessment of existing catalysts, and the utility of CNNs
    to predict and modulate adsorption energies \(E_{\text{ads}}\) using eDOS as input.
    eDOS occlusion and shifting experiments are conducted to extract chemical information from CNN model.}
    \label{main_fig1:pipeline}
\end{figure}
